Rationality, Evolution \& the Environment

### 2015-10-04 paper/paper.tex
restructuring and minor edits

We focus here on symmetric games with two players. A two-player game is symmetric if An example
is given in Figure~\ref{coordgame1}. \textcolor{red}{EXPAND}

\begin{itemize}
\item include here: minimax and choice given a belief
\end{itemize}

>>>>

We focus here on symmetric games with two players. A two-player game is symmetric if players
have the same action set, $A_1 = A_2$, and payoffs are symmetric:
$\pi_1(\myact{k}, \myact{l}) = \pi_2(\myact{l}, \myact{k})$ for all $k$ and $j$. An example is
given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
for player choosing the row against an opponent who chooses the column acts. Since the game is
symmetric, it suffices to give just these numbers. A rational player would choose $I$ exactly
when he beliefs that his opponent will choose $I$ with a probability at least
$\nicefrac{2}{3}$.

If an agent does not have a concrete probabilistic belief, the \emph{minimax rule} would tell
him to choose act $\act^*$ only if it maximizes payoffs for all worst case scenarios, i.e.,
$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
\myact{j})$.
Yet another option is to follow \emph{Laplace's rule} which is to choose $\act^*$ only if
$\act^* \in \argmax_{a \in A}  \sum_{a'} \pi(a, a')$. Laplace's rule is to rationally choosing under a
\emph{flat belief} that assigns equal probability to all of the opponent's choices.
